Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density

### 2018-05-30 manuscript.tex
finished sect 4

\xavier{Fig.~\ref{fig:faculae} shows the barycentric variation of the CCF induced by a simulated equatorial faculae of size 3\% relative to the visible stellar hemisphere. We compare the barycentric variation as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). Although the different estimates for the RV present similar variation as a function of rotational phase, we note that SN mean RV present a smaller amplitude than the two others.}

@@

\xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates. As we can see, the strength of the correlation between $\gamma$ and SN mean RV is extremely similar to the correlation between BIS SPAN and the RV, with a Pearson correlation coefficient} \xavier{$R=-0.75$}. \xavier{Moreover, the correlation between $\gamma$ and SN median RV is much stronger, reaching} \xavier{$R=-0.95$}. \xavier{When comparing the correlation between the width and the different RV estimates, we observe that the data draw a circle, which implies a phase shift between those two parameters. In this case we find no correlation between those parameters, however, the different estimates gives very similar results.}

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficient in in th ecase of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
\xavier{To modify with respect to the new results. It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae. In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.}

@@

\umberto{Specify characteristic of the spot.}\xavier{}

Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star. Similarly to the previous case, the presence of the spot leads to spurious variations in RV's for all the proposed indicators, but SN mean RV seems to have the smallest ones. We note however that in this case all the three indicators are similarly effected by the spurious changes in RV's caused by the spot.

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and respectively SN mean RV, SN median RV and RV. The correlation between $\gamma$ and SN median RV is equal to $-0.89$ while the correlation between $\gamma$ and SN median RV is equal to $-0.82$. Both these correlations are stronger than the correlation between the BIS SPAN and RV ($R^2=-0.77$). The correlations between the width of the CCF and the corresponding RV's are slightly stronger when fitting a SN rather than a Normal density, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}. The results show anyway a correlation close to $0$ when focusing on the width of the CCF, suggesting that the presence of a spot on the photosphere of star leads to changes in the shape of the CCF rather than its width.

@@

As before, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}. Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot. The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). The main differences respect to the previous case are that the parameter $\beta_{3}$, associated with $\gamma$, and the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM), are statistically significant to explain spurious variations caused by a spot. This information could be useful in the future for disentangle spots from facuale.

@@

The last presented simulation example consists in having not only spurious variations in RV's caused by the presence of a spot on the photosphere of the star but also a pure Doppler-shift because of an artificially injected planet. The purpose of this example is to check if we are able to disentangle the two different sources of variations in the set of RV's.

Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected. The planet, having an amplitude of 10 \ms, produces a pure Doppler-shift on the CCF, without further changing its shape.  In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet. %The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: SN mean RV has the largest related uncertainties and the standard errors associates with SN median RV are $10 \%$ smaller than the standard errors derived for RV.

Fig.~\ref{fig:spot.plus.planet.corr} shows the correlations between $\gamma$ and respectively SN mean RV and SN median RV and the correlation between BIS SPAN and RV. In this case the correlations are weaker than the ones derived when only a spot is present on the photosphere of the star. Anyway the $\gamma$ parameter shows a correlation with the median SN of $-0.433$, which is stronger than what the correlation between the other asymmetry indicators and their corresponding RVs. The correlations between the width of the CCF and the corresponding RV's are comparable and, similarly to the previous case, close to $0$.

@@

In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\ref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet. Hence, rather than just using Eq.~\ref{eq:RV:correction} we add the following keplerian function, which represents the pure Doppler-shift of the exoplanet under the assumption of circular orbit:
%
\begin{equation}
RV_{\text{exoplanet}}= K \sin \left(\frac{2 \pi}{P} (t - t_{0})\right),
\label{eq:RV:correction.planet}
\end{equation}
%
where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the presence of the exoplanet. Overall, the variations in RV's of the star can be defined as
%
\begin{equation}
RV= RV_{\text{stellar activity}} + RV_{\text{exoplanet}}.
\label{eq:RV:correction.overall}
\end{equation}
%

We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion. Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically. %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}. We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure Doppler-shift due to the planet. 
The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, are significant. We note in particular that the p--value associate to the amplitude parameter $K$ is $2e-16$. This result can be justify by the fact that the planet artificially injected has amplitude $K=10 \ms$.

%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
%   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity. In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet. The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}. In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
%    \label{fig:spotplanet.correction}
%\end{figure*}

@@

In this Sec.\ref{sec:soap} we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP. Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations. First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used. This is a bit surprising, since as the shape of the CCF changes, we expect SN median RV to be more robust than SN mean RV. \umberto{A possible justification of this ...}. As second, when searching for stellar activity by deriving the correlation between the set of RV's and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot. When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star. Related to these last two considerations, we note that the interaction between the asymmetry and the width of the CCF is useful to explain part of the variability in the RV's if the active region is a spot but not when it is a faculae. The proposed function to correct for stellar activity addressed high level of spurious variations in RV's caused by active regions. In particular, respect to other common linear interpolation, we proposed to use as covariates also the amplitude parameter of the CCF and the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM). As a consequence of using the interaction between the asymmetry and the width of the CCF, we note that the FWHM (or SN FWHM) becomes statistically not significant, while this is not the case if the interaction term is not involved in the linear regression. Finally, the correlations involving the common indicators (i.e. RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this density could be helpful when searching for active regions. We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.

@@

In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the approach based on the Normal density. Other four stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}. For all the stars that have been considered in the present work, we selected those CCF's having SNR larger than 10.

 A comparison with the results obtained by the classic approach is done, where the RV's of the star are estimated by retrieving the mean of the Normal density used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}. The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.

@@

A total of $1808$ CCF's measured in $2010$ have been analysed from the star Alpha Centauri B. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCF's, we performed the same selection as presented in \citet{Dumusque-2012}. Moreover, as noted in \citet{Dumusque-2012} and \citet{Thompson-2017}, this dataset presents a strong stellar activity signal.

We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $0.954$. This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of \kms. In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide a physical meaning to $\gamma$.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. Because $\gamma$ is adimensional, retrieving the slope between $\gamma$ and the BIS SPAN, which is expressed in \kms, allows us to provide physical meaning to $\gamma$.}
   \label{fig:alphacent:corr.gamma}
\end{figure}
%

Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RV's retrieved using the SN shape and the ones obtained with the Normal shape. It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}. When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{(top) RV's as function of Julian Day for Alpha Centauri b. The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
   \label{fig:alphacent:diff:RV}
\end{figure*}
%

>>>>

\xavier{To see the impact of a faculae on the different parameters of the CCF, we simulated the effect of an equatorial faculae of size 3\% relative to the visible stellar hemisphere. The faculae is face on when the phase equals to 0. Note that a 3\% faculae is relatively big for the Sun. At maximum activity, big faculae have generally a size of 1\%.
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is slightly different with respect to the two others, with a maximum amplitude happening at a different phase.}

@@

\xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates. As we can see, the strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are much stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively. Regarding the width barycenter correlations, we also find a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV, $R=0.98$ and 0.84, respectively. In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$. This first analysis shows that in the case of a faculae, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters seems to be better

probe better stellar activity. We will of course confirm this in the next sections presenting the case of a spot and of a spot plus a planet, but also in Sec~\ref{sec:4} when we will apply the SN fitting to real data sets.}

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95. In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
We see a slightly smaller rms after correction for the SN parameters, however the different is not significant. When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e. a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2. Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}

@@

\xavier{In this section, we simulate the effect on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere. The spot is face on when the phase equals to 0. Note that this is an extremely big spot for the Sun, as in general big spots are more in the regime of 0.1\%.
In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot. Contrary to the case of the faculae seen before, for the spots, all the different estimates of the CCF barycenter have exactly the same shape in variation. The amplitude for SN mean RV is however slightly smaller.}

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter: SN mean RV, SN median RV and RV. \xavier{The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed then by the correlation BIS SPAN -RV and $\gamma$-SN mean RV, with $R=0.86$. Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed. Once again, like in the case of the faculae, we see that some parameters of the SN gives stronger correlation than when using the Normal parameters.}

@@

As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

@@

The last simulation presented consists in having a planetary signal influencing the CCF, in addition to the 1\% spot modeled before (see Sec.~\ref{sec:soap.spot}). \xavier{The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit the the CCF. In this case, we inject a planet with an semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to 1/3rd of the stellar rotational phase.}

Fig.~\ref{fig:spot.plus.planet} shows the variation observed in the CCF barycenter parameters. Like in the case of the spot, all barycenter indicators show very similar variations, with SN mean RV showing a slightly smaller amplitude.

In Fig.~\ref{fig:spot.plus.planet.corr}, we show the correlation between the different CCF parameters. \xavier{Except of seing smaller correlation than in the case of the spot, due to the fact that the planet induces changes in the CCF barycenter without any change in any of the width or asymmetry parameters, the correlation strengths between the asymmetry parameters and the CCF barycenter are in exactly the same order than in the case of the spot: $\gamma$--SN median RV $R=-0.84$, BIS SPAN-RV $R=-0.78$ and $\gamma$--SN mean RV $R=-0.76$. The variation seen in the width-CCF barycenter space draw a circle like in the case of a spot, therefore, no correlation is observed between those parameters.}

@@

In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet. The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
%
\begin{equation}
RV= RV_{\text{stellar activity}} + RV_{\text{planet}},
\label{eq:RV:correction.overall}
\end{equation}
%
\xavier{where $RV_{\text{stellar activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
%
\begin{equation}
RV_{\text{exoplanet}}= K \sin \left(\frac{2 \pi}{P} (t - t_{0})\right),
\label{eq:RV:correction.planet}
\end{equation}
%
where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the planetary orbit.

%We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion. Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically. %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}. We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure Doppler-shift due to the planet. 
The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, \xavier{shows that except for the width parameters with coefficient $\beta_3$, all the other are significantly useful to explain the RV variation induce by a spot plus a planet.}
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
%   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity. In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet. The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}. In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
%    \label{fig:spotplanet.correction}
%\end{figure*}

@@

In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation.

\xavier{is all this discussion really usefull ? Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations. First of all, looking ad the analyses conducted with SOAP 2.0, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used. This is a bit surprising, since as the shape of the CCF changes, we expect SN median RV to be more robust than SN mean RV. \umberto{A possible justification of this ...}. As second, when searching for stellar activity by deriving the correlation between the set of RV's and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot. When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star. Related to these last two considerations, we note that the interaction between the asymmetry and the width of the CCF is useful to explain part of the variability in the RV's if the active region is a spot but not when it is a faculae. The proposed function to correct for stellar activity addressed high level of spurious variations in RV's caused by active regions. In particular, respect to other common linear interpolation, we proposed to use as covariates also the amplitude parameter of the CCF and the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM). As a consequence of using the interaction between the asymmetry and the width of the CCF, we note that the FWHM (or SN FWHM) becomes statistically not significant, while this is not the case if the interaction term is not involved in the linear regression. Finally, the correlations involving the common indicators (i.e. RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this density could be helpful when searching for active regions. We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.}

@@

In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}. For all the stars that have been considered in the present work, \xavier{we selected CCFs  that were derived from spectra that had a SNR at 550 nm larger than 10.}

% A comparison with the results obtained by the classic approach is done, where the RV is estimated by retrieving the mean of the Normal density used to fit the CCF, along with the FWHM of the Normal density and the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}. The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.

@@

We analysed the $1808$ RV observations of Alpha Centauri B taken in 2010 by the HARPS spectrograph. Note that more observation have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}. \xavier{We choose these observations as their represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}

We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN. \xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signals seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $R=0.95$.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. Because $\gamma$ is adimensional, retrieving the slope between $\gamma$ and the BIS SPAN, which is expressed in \kms, allows us to provide physical meaning to $\gamma$.}
   \label{fig:alphacent:corr.gamma}
\end{figure}
%

Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density. It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}. When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{(top) RV's as function of Julian Day for Alpha Centauri b. The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
   \label{fig:alphacent:diff:RV}
\end{figure*}
%
